Safe Transferable Regions

### 2017-01-05 paper/related.tex
added alloc context to constraint generation rules

Our region type system can also be thought of as a specialized
ownership type system~\cite{OwnershipSurvey}, where each region is the
owner of all objects allocated in the region.
%
An ownership type system for safe region-based memory management in
real-time Java has been proposed by~\cite{MIT03}.  
% Like us, they too assume a source language with programmer-managed
% memory regions, and focus on proving safety of programs written in
% that language.  
Their language permits only lexically-scoped (stack) regions
(in the context of shared-memory concurrency). In contrast, we permit
regions with dynamically determined lifetimes (in the context of message-passing concurrency).
% We borrow outlives relation from their formal
% development, and our type system bears some similarities to theirs.
Our language also admits generics and higher-order functions.
We also establish type safety and transfer safety results that
formalize the guarantees provided by our system. While~\cite{MIT03}'s
language is explicitly typed, our language comes equipped with full
type inference.

>>>>

Our region type system can also be thought of as a specialized
ownership type system~\cite{OwnershipSurvey}, where each region is the
owner of all objects allocated in the region.
%
An ownership type system for safe region-based memory management in
real-time Java has been proposed by~\cite{MIT03}.  
% Like us, they too assume a source language with programmer-managed
% memory regions, and focus on proving safety of programs written in
% that language.  
Their language permits only lexically-scoped (stack) regions.
% (in the context of shared-memory concurrency).
In contrast, we permit regions with dynamically determined lifetimes.
% (in the context of message-passing concurrency).
% We borrow outlives relation from their formal
% development, and our type system bears some similarities to theirs.
Our language also admits generics and higher-order functions.
We also establish type safety and transfer safety results that
formalize the guarantees provided by our system. While~\cite{MIT03}'s
language is explicitly typed, our language comes equipped with full
type inference.
